---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {tidysec}

<!-- badges: start -->
<!-- badges: end -->

The goal of {tidysec} is to facilitate working with filings provided by the American Securities and Exchange Commission. Currently the package only supports 13F-filings.

## Installation

You can install the development version of {tidysec} from [Github](https://github.com/balthasars/tidysec) with:

``` r
devtools::install_github("balthasars/tidysec")
```

## Retrieve and parse a 13F-filing

Use `get_13f()` for that purpose.
This function returns the filings as a tibble with a nested data frame column.

```{r example}
library(tidysec)
library(magrittr)
cik_blackrock <- "1364742"
br_2015 <- get_13f(cik = cik_blackrock, year = 2015, clean_col_names = FALSE, amendments = FALSE)
br_2015
```

To work with the filing(s), use `tidyr::unnest()`:

```{r}
br_2015 %>% 
  tidyr::unnest(filing)
```


Amendments to 13F filings (13F-HR/A) cannot be parsed yet.
However, you can still get the link to their .txt file by setting `link_only = TRUE` and `amendments = TRUE`:

```{r}
cik_blackrock <- "1364742"
get_13f(cik = cik_blackrock, year = 2015, link_only = TRUE, amendments = TRUE)
```


## Get a list of all SEC filings by a company

Let's say you wanted a list of all of Credit Suisse AG's 2020 company filings. 

```{r}
cik_credit_suisse <- "824468"
cs_2019 <- get_list_of_filings(
  cik = cik_credit_suisse, 
  year = 2020, 
  filing_type = "all",
  clean_col_names = TRUE 
  )
cs_2019
```
