---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {tidysec}

<!-- badges: start -->
<!-- badges: end -->

The goal of {tidysec} is to facilitate working with filings provided by the American Securities and Exchange Commission. Currently the package only supports 13F-filings.

## Installation

You can install the development version of {tidysec} from [Github](https://github.com/balthasars/tidysec) with:

``` r
devtools::install_github("balthasars/tidysec")
```

## Parse a 13F-filing

To parse a 13F-filing you need the link to the filing made to the SEC.
To obtain the links to all filings of a given company use `get_filings_info()` (not shown here),

```{r example}
library(tidysec)
snb_q1_2016_13f <- "https://www.sec.gov/Archives/edgar/data/1582202/000158220216000006/InfoTable_Q12016.xml"
get_filing(snb_q1_2016_13f)
```
